API design for machine learning software: experiences from the scikit-learn project

### 2013-09-27 paper.tex
stress early on that user-defined estimators are first-class citizens
Someone at ECML wisely remarked that this is a requirement for a truly
compositional library.

\begin{description}
  \item[Consistency.]
       All objects (basic or composite) share a consistent interface composed of
       a limited set of methods. This interface is documented in a consistent
       manner for all objects.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored and exposed as public attributes.
  \item[Non-proliferation of classes.]
       Learning algorithms are the only objects to be represented using custom classes.
       Datasets are represented as NumPy arrays or SciPy sparse matrices.
       Hyper-parameter names and values are represented as standard
       Python strings or numbers whenever possible.
       This keeps \sklearn easy to use and easy to combine with other libraries.
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parametrized on other algorithms.
       Whenever feasible, such algorithms are implemented and composed from
       existing building blocks.
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       an appropriate default value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

>>>>

\begin{description}
  \item[Consistency.]
       All objects (basic or composite) share a consistent interface composed of
       a limited set of methods. This interface is documented in a consistent
       manner for all objects.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored and exposed as public attributes.
  \item[Non-proliferation of classes.]
       Learning algorithms are the only objects to be represented using custom classes.
       Datasets are represented as NumPy arrays or SciPy sparse matrices.
       Hyper-parameter names and values are represented as standard
       Python strings or numbers whenever possible.
       This keeps \sklearn easy to use and easy to combine with other libraries.
  \item[Composition.]
       Learning algorithms can be combined into processing pipelines.
       Ensemble methods and other meta-algorithms
       are implemented as adapter classes.
       User-defined algorithms that follow the right conventions
       can be used as building blocks in the resulting composite algorithms.
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       an appropriate default value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}
